%-----------PROJECTS-----------
\vspace{-6.5mm}
\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Pollaris \textbar{} Cloud-Native Enterprise Polling Platform}}{May 2026}
\vspace{-4.5mm}
\resumeItemListStart
\resumeItem{Engineered fault-tolerant voting modules using Firestore ACID Transactions, eliminating race conditions during concurrent updates and strictly enforcing one-vote-per-user constraints to guarantee 100\% data integrity.}
\resumeItem{Architected a robust state-machine to manage strict entity lifecycles and engineered server-side access control lists using Next.js 16 Server Actions to mathematically isolate private data environments.}
\resumeItem{Established an automated CI/CD pipeline via GitHub Actions and Docker, orchestrating secure, multi-stage stateless builds to reliably publish enterprise-ready artifacts to the GitHub Container Registry (GHCR).}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{IoT Smart Parcel Locker \textbar{} Cloud-Integrated Logistics}}{Feb 2026}
\vspace{-4.5mm}
\resumeItemListStart
\resumeItem{Validated the seamless synchronization between embedded C/C++ microcontrollers (Arduino/NodeMCU) and Adafruit IO, ensuring highly reliable real-time tracking of automated locker occupancy via cloud dashboards.}
\resumeItem{Designed comprehensive security testing for a 2FA locker access mechanism, validating dynamic One-Time Password (OTP) generation and simulated breach scenarios to strictly enforce remote access denial workflows.}
\resumeItem{Evaluated dynamic resource automation capabilities by applying digital filtering algorithms to eliminate sensor latency, reducing GSM SMS notification latency to under 6 seconds.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI Wide Area Surveillance \textbar{} Cloud-Edge Threat Intelligence}}{Jan 2026 -- Mar 2026}
\vspace{-4.5mm}
\resumeItemListStart
\resumeItem{Deployed a deep learning YOLOv8 inference pipeline onto edge hardware, integrated with an OpenCV feature-matching algorithm to dynamically construct seamless panoramic views and automate real-time human detection.}
\resumeItem{Engineered a low-latency, remote cloud-alerting pipeline via SMTP servers and developed a dynamic Flask web dashboard to securely render edge-processed threat analytics to centralized monitoring environments.}
\resumeItem{Architected an intelligent, modular edge computing framework featuring selective data storage protocols to maximize local storage efficiency and enable future integration with AWS and Firebase data streams.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{BusPulse \textbar{} Live Public Transit Tracking Platform}}{April 2026 -- Present}
\vspace{-4.5mm}
\resumeItemListStart
\resumeItem{Engineered a student-first live bus tracking application using TypeScript, designed to eliminate transit guesswork and optimize daily commute planning for university students.}
\resumeItem{Implemented real-time geolocation services and dynamic route mapping to provide accurate departure predictions, significantly improving the user experience over standard static schedules.}
\resumeItem{Deployed the full-stack architecture on Vercel, ensuring high availability, rapid load times, and a seamless mobile-first interface for concurrent active users.}
\resumeItemListEnd

\resumeSubHeadingListEnd
